The Latent Constructive Rewrite Model \\ or \\ The Latent Conceptual Grammar Model

### 2014-10-10 drafts/cfp/draft.tex
Changes to draft and initial bib file for draft.

\section{Abstract}
How do people learn systems of related concepts from data? Consider,
for example, a school-age child's knowledge of number. This knowledge
supports a large number of related operations: the child knows which
words denote numbers, how to use those words to label cardinalities of
sets, how to translate between digit representations and word
representations of number, how to compare cardinalities, etc. The
child knows how to perform these operations over an unbounded set of
elements, even though the data that underlies this knowledge is small
and noisy. Here we propose that such systems of related concepts can
be learned via hierarchical probabilistic inference over probabilistic
string rewrite systems (PSRS) -- a mildly context-sensitive class of
probabilistic string gramamrs that corresponds to a restricted
fragment of stochastic logic programs (SLPs). Specifically, we extend
the variational expectation-maximization algorithm for Hierarchical
Dirichlet PCFGs to accomodate PSRSs. This algorithm we present enables
a tractible compromise between highly restrictive context-free
knowledge representations and the intractability of performing similar
inference procedures over general logic programs. Empirically, we show
how such restricted string rewrite systems can capture non-trivial
conceptual knowledge and how our algorithm is able to learn such
knowledge from data.

@@

\section{Abstract 3}
Evidence: 
  - ``the number after twenty seven is twenty six''
  -

>>>>

\section{Abstract}
A popular approach in statistical machine learning is to automatically
find the latent \emph{features} of the data that are most relevant or
informative. But a latent feature based view of concept learning does
not match up naturally with the structured symbolic knowledge that
seems to underlie people's understanding of many domains. How can we
combine the flexibility, noise tolerance, and computational
practicality of latent feature based statistical machine learning with
the symbolic knowledge representations that best capture human
understanding? Here present a learning model we dub Latent Concept
Grammars (LCGs) as a proposal. An LCG is a densely connected set of
probabilistic string rewrite rules over an initially uninterpreted set
of predicates. When fit to data using a hierarchical Bayesian prior,
these predicates assume the roles of informative latent concepts. This
approach allows us to learn knowledge that is stochastic and
recursively structured while maintaining computational
tractability. We show how learning in LCGs can be implemented using
the probabilistic logic programming system PRISM, and we present
preliminary experiments.

How do people learn systems of related concepts from
data?  Consider, for example, a school-age child's knowledge of
number. This knowledge supports a large number of related operations:
the child knows which words denote numbers, how to use those words to
label cardinalities of sets, how to translate between digit
representations and word representations of number, how to compare
cardinalities, etc. The child knows how to perform these operations
over an unbounded set of elements, even though the data that underlies
this knowledge is small and noisy. Here we propose that such systems
of related concepts can be learned via hierarchical probabilistic
inference over probabilistic string rewrite systems (PSRS) -- a mildly
context-sensitive class of probabilistic string gramamrs that
corresponds to a restricted fragment of stochastic logic programs
(SLPs). Specifically, we extend the variational
expectation-maximization algorithm for Hierarchical Dirichlet PCFGs to
accomodate PSRSs. This algorithm we present enables a tractible
compromise between highly restrictive context-free knowledge
representations and the intractability of performing similar inference
procedures over general logic programs. Empirically, we show how such
restricted string rewrite systems can capture non-trivial conceptual
knowledge and how our algorithm is able to learn such knowledge from
data.

@@

\section{Abstract 3}
